### 2023-07-19 paper-reviews/papers-2023.tex
Add CGC Monitor reference

    The article describes a standard way of adding new processor instructions purely based on instruction count: find a pattern, add instruction, makes sure it works, measure instruction count to estimate how performance changes, repeat it needed. The approach is applied to RISC-V processors using IMPERAS ISS. Could be a good reference for students who are not aware how this could be done.
\end{itemize}

>>>>

    The article describes a standard way of adding new processor instructions purely based on instruction count: find a pattern, add instruction, makes sure it works, measure instruction count to estimate how performance changes, repeat it needed. The approach is applied to RISC-V processors using IMPERAS ISS. Could be a good reference for students who are not aware how this could be done.

    \item \cite{Thompson:CGCMonitor:2018}:

    The article is a good demonstration of what can be achieved using analysis capabilities provided by a simulation system. Authors of the paper built vetting system for a cyber challenge. The main purpose of the system was to make sure that none of the competitors is trying to subvert the competition infrastructure. The vetting system was build on top of Simics hap and breakpoint capabilities thus providing non-intrusive analysis with support for reverse execution.
\end{itemize}
